Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils

### 2016-02-11 manuscript/cpcrw_manuscript.Rmd
Added volumetric WC data and results

* Core BD

@@

* Soil WC changes over incubation

```{r wc, echo=FALSE}
# wc and wc_alltrt are computed by 5-analyze.R script
wcbegin <- subset(wc_alltrt, stage == "Beginning")
wcend <- subset(wc, stage == "End")
wcendmean <- wcend$mean
names(wcendmean) <- wcend$Treatment
wcendsd <- wcend$sd
names(wcendsd) <- wcend$Treatment
```

Gravimetric water content was `r pn(wcbegin$mean, 2)` ± `r pn(wcbegin$sd, 2)` (min `r pn(wcbegin$min, 2)`, max `r pn(wcbegin$max, 2)`) at the beginning of the incubation (**Figure 1**). "Field moisture" cores were on average unchanged (`r pn(wcendmean["Field moisture"], 2)` ± `r pn(wcendsd["Field moisture"], 2)`) at the end of the incubation, but both the drought treatments, which did not differ from each other in their effect on gravimetric water content, had declined to `r pn(wcendmean["Drought"], 2)` ±  `r pn(wcendsd["Drought"], 2)`.

>>>>

@@

```{r wc, echo=FALSE}
# wc and wc_alltrt are computed by 5-analyze.R script
gwcbegin <- subset(gwc_alltrt, stage == "Beginning")
gwcend <- subset(gwc, stage == "End")
gwcendmean <- gwcend$mean
names(gwcendmean) <- gwcend$Treatment
gwcendsd <- gwcend$sd
names(gwcendsd) <- gwcend$Treatment
vwcbegin <- subset(vwc_alltrt, stage == "Beginning")
vwcend <- subset(vwc_alltrt, stage == "End")
```

Gravimetric water content was `r pn(gwcbegin$mean, 2)` ± `r pn(gwcbegin$sd, 2)` (min `r pn(gwcbegin$min, 2)`, max `r pn(gwcbegin$max, 2)`) at the beginning of the incubation (**Figure 1**). "Field moisture" cores were on average unchanged (`r pn(gwcendmean["Field moisture"], 2)` ± `r pn(gwcendsd["Field moisture"], 2)`) at the end of the incubation, but both the drought treatments, which did not differ from each other in their effect on gravimetric water content, had declined to `r pn(gwcendmean["Drought"], 2)` ±  `r pn(gwcendsd["Drought"], 2)`. Volumetric water content values ranged from `r pn(vwcbegin$mean, 2)` ± `r pn(vwcbegin$sd, 2)` (min `r pn(vwcbegin$min, 2)`, max `r pn(vwcbegin$max, 2)`) at the beginning of the experiment to `r pn(vwcend$mean, 2)` ± `r pn(vwcend$sd, 2)` (min `r pn(vwcend$min, 2)`, max `r pn(vwcend$max, 2)`) at the end.
